\documentclass{article}[10pt]
% An example of defining macros
\include{../general_version/preamble.tex}
\usepackage{etaremune}
\title{\vspace{-.8cm} \centering Publication List}
\author{
Robert Baraldi (rjbaral@sandia.gov) \\
Uncertainty Quantification and Optimization, Sandia National Laboratories\footnote{\tiny Note that Sandia National Laboratories' Review and Approval process may prevent some of this work from being publically available on ArXiv until cleared. This in-review but not cleared work will be denoted via $*$. }}

\begin{document}
\maketitle
\thispagestyle{firstpage}

\subsection*{In Review$^*$}
\begin{etaremune}
\item Harbir Antil, {\bf Robert Baraldi}, Rohit Khandelwal, Drew Kouri (2025), ``An Adaptive Finite Element Trust-Region Method for Regularized PDE-Constrained Optimization'', \emph{SIAM Journal on Scientific Computing}.
\item {\bf Robert Baraldi}, Aurya Javeed, Drew P. Kouri, Katya Scheinberg (2025), ``\href{https://arxiv.org/abs/2510.03187}{ProxSTORM -- A Stochastic Trust-Region Algorithm for Nonsmooth Optimization}''. \emph{Computational Optimization and Applications}.
\item {\bf Robert Baraldi}, Michael Hinterm{\"u}ller, Qi Wang (2025) ``A Multilevel Proximal Trust-Region Method for Nonsmooth Optimization with Applications to Scientific Machine Learning''. \emph{Optimization Methods and Software}.
\end{etaremune}
 \hrule
\vspace{1em}
\subsection*{Peer-Reviewed}
\noindent
\begin{etaremune}
  \item Harbir Antil, {\bf Robert Baraldi}, Drew Kouri (2024), ``Adaptive Randomized Sketching for Dynamic Nonsmooth Optimization'', \emph{Optimization and Engineering} (to appear).
  \item {\bf Robert Baraldi}, Stefan Wild, Sven Leyffer (2023), ``\href{https://optimization-online.org/2024/02/using-filter-methods-to-guide-convergence-for-admm-with-applications-to-nonnegative-matrix-factorization-problems/}{Using Filter Methods to Guide Convergence for ADMM with Applications to Nonnegative Matrix Factorization}'' \emph{Journal of Optimization Theory and Applications} (to appear).
  \item  {\bf Robert Baraldi}, Paul Manns,  ``\href{https://epubs.siam.org/doi/full/10.1137/24M170466X}{Coordinate Descent for Total-Variation Integer Optimal Control}'', \emph{SIAM Journal on Control and Optimization} 63(6), 3825--3855.
  \item  {\bf Robert Baraldi}, Drew P. Kouri (2025), ``\href{https://link.springer.com/article/10.1007/s10589-024-00628-x}{Efficient Proximal Subproblem Solvers for a Nonsmooth Trust-Region Method}'', \emph{Computational Optimization and Applications} 90, 193-226.
  \item  {\bf Robert Baraldi},  Drew P. Kouri (2024), ``\href{https://link.springer.com/article/10.1007/s11590-023-02092-8}{Local Convergence Analysis of an Inexact Trust-Region Method for Nonsmooth Optimization}'', \emph{Optimization Letters} 18, 663-680.
  \item  {\bf Robert Baraldi}, Aleksandr Aravkin, Dominique Orban (2024), ``\href{https://doi.org/10.1137/22M1538971}{A Levenberg - Marquardt Method for Nonsmooth Regularized Least Squares}'',  \emph{SIAM Journal on Scientific Computing} 46(4), A2557-A2581.
  \item  {\bf Robert Baraldi}, Drew P. Kouri (2023), ``\href{https://link.springer.com/article/10.1007/s10107-022-01915-3}{A Proximal Trust-Region Method for Nonsmooth Optimization with Inexact Function and Gradient Evaluations}'', \emph{Mathematical Programming.} 201(1), 559-598.
  \item  Christopher Liu, Donsub Rim, {\bf Robert Baraldi}, Randall LeVeque, Kenjiro Terada (2022), ``\href{https://agupubs.onlinelibrary.wiley.com/doi/full/10.1029/2022GL099511}{Tsunami Early Warning from Global Navigation Satellite System Data using Convolutional Neural Networks}'' \emph{Geophysical Review Letters.} 49(20).
  \item  {\bf Robert Baraldi}, Aleksandr Aravkin, Dominique Orban (2021), ``\href{https://epubs.siam.org/doi/abs/10.1137/21M1409536}{A Proximal Quasi-Newton Trust-Region Method for Nonsmooth Regularized Optimization}'', \emph{SIAM Journal of Optimization.} 32(2): 900-929.
  \item  Christopher Liu, Donsub Rim, {\bf Robert Baraldi}, Randall LeVeque (2021), ``\href{https://link.springer.com/article/10.1007/s00024-021-02841-9}{Comparison of Machine Learning Approaches for Tsunami Forecasting from Sparse Observations}'', \emph{Pure and Applied Geophysics} 178, 5129-5153.
  \item  {\bf Robert Baraldi}, Rajiv Kumar, Aleksandr Aravkin  (2019), ``\href{https://ieeexplore.ieee.org/document/8861392}{Basis Pursuit Denoise with Nonsmooth Constraints}'', \emph{IEEE Transactions on Signal Processing} 67(22): 5811-5823.
  \item  {\bf Robert Baraldi}, Carl Ulberg, Rajiv Kumar, Kenneth Creager, Aleksandr Aravkin (2019), “\href{https://iopscience.iop.org/article/10.1088/1361-6420/ab3204}{Relaxation Algorithms for matrix completion, with applications to seismic travel-time data interpolation}'', \emph{Inverse Problems} 35(10):105009.
  \item  Harvey Thomas Banks, {\bf Robert Baraldi}, Jared Catenacci, Nicholas Myers (2016), “\href{https://www.ncsu.edu/crsc/reports/ftp/pdf/crsc-tr16-04.pdf}{Parameter Estimation Using Unidentified Individual Data in Individual Based Models}''. \emph{Mathematical Modeling of Natural Phenomena} 11(6):103-121.
  \item  Harvey Thomas Banks, {\bf Robert Baraldi}, Kevin Flores, Michael Stemkovski (2016), “\href{http://www.mdpi.com/2076-3417/6/5/155/htm}{Validation of a Mathematical Model for Green Algae (\emph{Raphidocelis subcapitata}) Growth and Implications for a Coupled Dynamical System with \emph{Daphnia Magna}}'', \emph{Applied Sciences} 6(5): 155.
  \item  Kaska Adoteye, Harvey Thomas Banks, {\bf Robert Baraldi}, John Nardini, W Clay Thompson (2015), “\href{http://www.ijpam.eu/contents/2015-105-3/16/16.pdf}{Correlation of Parameter Estimators for Models Admitting Multiple Parametrizations}'', \emph{International Journal of Pure and Applied Mathematics} 105(3): 497-522.
  \item  Harvey Thomas Banks, {\bf Robert Baraldi}, Kevin Flores (2015), ``\href{http://www.ncsu.edu/crsc/reports/ftp/pdf/crsc-tr15-03.pdf}{Optimal Design for Minimizing Uncertainty in Dynamic Equilibrium Systems}'', \emph{Eurasian Journal of Mathematical and Computer Applications} 3: 20-43.
  \item  Harvey Thomas Banks, {\bf Robert Baraldi}, Karissa Cross, Christina McChesney, Laura Poag, Emma Thorpe, Kevin Flores (2015), “\href{http://aimsciences.org/journals/displayArticlesnew.jsp?paperID=11300}{Uncertainty quantification in modeling HIV viral mechanics.}'', \emph{Mathematical Biosciences and Engineering} 12(5): 937-964.\\
\end{etaremune}
\hrule
\vspace{1em}
\subsection*{Book Chapters}
\begin{etaremune}
  \item Robert Baraldi, Drew Kouri, Denis Ridzal (2023), ``Trust-Region Methods with Inexact and Adaptive Computations'', \emph{Encyclopedia of Optimization}.\\
\end{etaremune}
\hrule
\vspace{1em}
\subsection*{Conference Proceedings}
\noindent
% \subsubsection*{2014}
\begin{etaremune}
  \item {\bf Robert Baraldi}, Evelyn Herberg, Drew P. Kouri, Harbir Antil (2023), ``Adaptive Randomized Sketching for Dynamic Nonsmooth Optimization'', \emph{Proceedings of the International Model Analysis Conference XLI: Model Validation and Uncertainty Quantification}, \#14609.
 \item {\bf Robert Baraldi}, Karissa Cross, Christina McChesney, Laura Poag, Emma Thorpe, Kevin Flores, Harvey Thomas Banks (2014) \href{http://ieeexplore.ieee.org/stamp/stamp.jsp?tp=&arnumber=6858714&isnumber=6858556}{Uncertainty quantification for a model of HIV-1 patient response to antiretroviral therapy interruptions.} \emph{Proceedings of the 2014 American Control Conference}, 2753-2758.\\
\end{etaremune}
\hrule\vspace{1em}
\subsection*{Conference Presentations and Talks}
\begin{etaremune}
  \item {\bf Robert Baraldi} (2025), ``An Adaptive Inexact Trust-Region Method for PDE-Constrained Optimization with Regularized Objectives'', PNWS-SIAM 2025, October 3-5, Seattle. \\
  \item Harbir Antil, {\bf Robert Baraldi}, Rohit Khandelwal, Drew P. Kouri (2025),  ``An Adaptive Finite Element Trust-Region Method for Regularized PDE-Constrained Optimization'', ICCOPT 2025, July 20-24, Los Angeles. \\
  \item Robert Baraldi, Michael Hinterm{\"u}ller, Drew P. Kouri (2025),  ``Optimization of Total Variation-Regularized Functions using Inexact Proximal Solves'', The 30th Biennial Numerical Analysis Conference, June 24-27, Glasgow. \\
  \item Harbir Antil, Robert Baraldi, Rohit Khandelwal, Drew P. Kouri (2025),  ``An Adaptive Finite Element Trust-Region Method for Regularized PDE-Constrained Optimization'', East Coast Optimization Meeting, April 17-18, Washington DC. \\
  \item Robert Baraldi (2025),  ``A Nonsmooth Trust-Region Framework for Applications in Data Science and PDE Constrained Optimization'', Simon Fraser University MOCAD Seminar, March 10, Vancouver, Canada. \\
  \item Robert Baraldi, Michael Hinterm{\"u}ller, Drew P. Kouri (2025),  ``Optimization of Total Variation-Regularized Functions using Inexact Proximal Solves'', SIAM CSE, March 3-7, Ft. Worth, TX. \\
  \item Harbir Antil, Robert Baraldi, Drew P. Kouri (2024),  ``Adaptive Randomized Sketching for Dynamic Nonsmooth Optimization'', INFORMS24, October 19-23, Seattle, WA. \\
  \item  {\bf Robert Baraldi}, Drew P. Kouri (2024),  ``A Proximal Trust-Region Method for Nonsmooth Optimization with Inexact Function and Gradient Evaluations'', WCOM24, September 21, Vancouver, Canada.
  \item  {\bf Robert Baraldi}, Drew P. Kouri, Harbir Antil (2024),  ``Adaptive Randomized Sketching for Dynamic Nonsmooth Optimization'', ISMP24, July 21-26, Mont{\'e}al, Canada.
  \item  {\bf Robert Baraldi}, Drew P. Kouri, Harbir Antil (2024),  ``Adaptive Randomized Sketching for Dynamic Nonsmooth Optimization'', PASC24, June 3-5, Zurich, Switzerland.
  \item  {\bf Robert Baraldi}, Aurya Javeed, Drew Kour, Christian Glusa, Kim Liegeois (2024),  ``Training Neural Networks with PyROL: Algorithms and Examples'', Copper Mountain Iterative Methods, April 14-19, Copper Mountain Co.
  \item  {\bf Robert Baraldi}, Drew P. Kouri, Harbir Antil (2024),  ``Adaptive Randomized Sketching for Dynamic Nonsmooth Optimization'', SIAM UQ, February 29 - March 1, Trieste, Italy.
  \item  {\bf Robert Baraldi}, Drew P. Kouri (2024),  ``A Proximal Trust-Region Method for Nonsmooth Optimization with Inexact Function and Gradient Evaluations'', Dept. of Mathematics Seminar, February 24, TU Dortmund, Germany.
  \item  {\bf Robert Baraldi}, Drew P. Kouri (2023),  ``A Proximal Trust-Region Method for Nonsmooth Optimization with Inexact Function and Gradient Evaluations'', Applied Inverse Problems, September 4, G{\"o}ttingen, Germany.
  \item  {\bf Robert Baraldi}, Drew P. Kouri (2023),  ``A Proximal Trust-Region Method for Nonsmooth Optimization with Inexact Function and Gradient Evaluations'', WIAS Research Seminar on Mathematical Optimization Nonsmooth Variational Problems and Operator Equations, August 29, Berlin, Germany.
  \item  {\bf Robert Baraldi}, Evelyn Herberg, Harbir Antil, Drew P. Kouri (2023), ``Adaptive Randomized Sketching for Dynamic Nonsmooth Optimization'', SIOPT, May 31 - June 4, Seattle, WA.
  \item  {\bf Robert Baraldi}, Drew P. Kouri (2023), ``Efficient Proximal Subproblem Solvers for an Inexact Nonsmooth Trust-Region Method'', SIAM CSE, February 28 - March 4, Amsterdam, ND.
  \item  {\bf Robert Baraldi}, Drew P. Kouri (2023),  ``An Inexact Trust-Region Algorithm for Nonsmooth Nonconvex Regularized Problems'', Bayreuth Applied Mathematics Seminar, February 24, Bayreuth, Germany.
  \item  {\bf Robert Baraldi}, Evelyn Herberg, Harbir Antil, Drew P. Kouri (2023), ``Adaptive Randomized Sketching for Dynamic Nonsmooth Optimization'', IMAX XLI, February 15, Austin, TX.
  \item  {\bf Robert Baraldi}, Drew P. Kouri (2022), ``An Inexact Trust-Region Algorithm for Nonsmooth Nonconvex Regularized Problems'', Centre de recherches math{\'e}matiques Seminar at McGill, October 24, Quebec.
  \item  {\bf Robert Baraldi}, Drew P. Kouri (2022), ``An Inexact Trust-Region Algorithm for Nonsmooth Nonconvex Regularized Problems'', GERAD Seminar, October 20, Polytechnique Montr{\'e}al, Quebec.
  \item  {\bf Robert Baraldi}, Drew P. Kouri (2022), ``An Inexact Trust-Region Algorithm for Nonsmooth Nonconvex Regularized Problems'', Center for Mathematics and Artificial Intelligence Colloquium, September 30 (Virtual).
  \item  {\bf Robert Baraldi}, Stefan Wild, Sven Lyeffer (2022), ``Using Filter Methods to Guide Convergence for ADMM, with Applications to Nonnegative Matrix Factorization Problems'', ICCOPT/MOPTA 2022, July 25-28. Bethlehem, PA.
  \item  {\bf Robert Baraldi}, Aleksandr Aravkin, Dominique Orban (2021), ``A Proximal Quasi-Newton Trust-Region Method for Nonsmooth Regularized Optimization'', SIOPT 2021 (virtual), July 22.
  \item  {\bf Robert Baraldi}, Stefan Wild, Sven Lyeffer (2020), ``Using Filter Methods to Guide Convergence for ADMM, with Applications to Nonnegative Matrix Factorization Problems'', SIAM CSE 2021, (Virtual).
  \item  {\bf Robert Baraldi} (2020), ``Moreau-Yoshida Regularization and First Order Methods with Firedrake'', Firedrake 2020, Seattle, WA; February 22.
  \item  {\bf Robert Baraldi} (2020), ``Basis Pursuit Denoise with Nonsmooth Constraints'', DOE CSGF Annual Program Review, Arlington, VA; July 14-18.
  \item  {\bf Robert Baraldi} (2019), ``An Acceleration Framework for Parameter Estimation using Implicit Sampling and Adaptive Reduced order Models'', SIAM CSE, Spokane WA; 2/25-3/1.
  \item  {\bf Robert Baraldi} (2019), ``Relaxation Algorithms for matrix completion, with applications to seismic travel-time data interpolation'', DOE CSGF Annual Program Review, Arlington, VA; July 15-19.
  \item  {\bf Robert Baraldi} (2016), ``Systems Modeling and Data Assimilation in Drug Development'', SIAM Annual Life Sciences Conference, Boston, MA; July 11-15.\\
\end{etaremune}
\hrule
\vspace{1em}
\subsection*{Technical Reports (Not peer-reviewed)}
\noindent
% \subsubsection*{2014}
\begin{etaremune}
  \item  {\bf Robert Baraldi}, John Nardini, Emma Thorpe, and Harvey Thomas Banks (2014) \href{ http://www.ncsu.edu/crsc/reports/ftp/pdf/crsc-tr14-07.pdf}{The Effects of Parameterization on Inverse Problems}, CRSC Technical report CRSC-TR14-07, Raleigh, NC.
  \item {\bf Robert Baraldi}, Karissa Cross, Christina McChesney, Laura Poag, Emma Thorpe, Kevin Flores, and Harvey Thomas Banks (2013) \href{http://www.ncsu.edu/crsc/reports/ftp/pdf/crsc-tr13-07.pdf}{``Mathematical Modeling of HCV Viral Kinetics''}. CRSC Technical report CRSC-TR13-07, Raleigh, NC.\\
\end{etaremune}
  \hrule
  \vspace{1em}
\section*{Open-Source Code}
\noindent
\href{https://rol.sandia.gov/}{Rapid Optimization Library}.\\
\href{https://github.com/JuliaSmoothOptimizers/RegularizedOptimization.jl/}{RegularizedOptimization} (part of \href{https://github.com/JuliaSmoothOptimizers}{JuliaSmoothOptimizers}).\\
\href{https://github.com/JuliaSmoothOptimizers/ShiftedProximalOperators.jl}{ShiftedProximalOperators} (part of \href{https://github.com/JuliaSmoothOptimizers}{JuliaSmoothOptimizers}).\\
\href{https://github.com/JuliaSmoothOptimizers/RegularizedProblems.jl/}{RegularizedProblems} (part of \href{https://github.com/JuliaSmoothOptimizers}{JuliaSmoothOptimizers}).\\
% \nocite{*}
% \bibliographystyle{unsrt}
% \bibliography{myreferences}

\end{document}



